Simultaneous Elicitation of Scoring Rule and Agents Preferences for Robust Winner Determination

### 2020-01-21 draft.tex
changes in strategy description

We also define the \strat{Extreme completions} strategy, which we consider as a more realistic baseline. 
Consider the solution of the minimax regret game, 
 $(x^{*},\bar{y},\bar{\profile},\bar{\w})$, where $x^{*}$ is the minimax regret optimal alternative, and $\bar{y} = \arg \max_{y \in A} \PMR(x,y; \pprofile, W)$, $\bar{\profile}$ and $\bar{\w}$ are the adversarial choices, thus, the instantiations that, given the choice of $x^*$, maximize the regret. 
Define: 
\begin{align}
\tau_{1} & = \min_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w),  \label{eq:tau1} \\
\tau_{2} & = \min_{\profile \in C(\pprofile)} s(\bar{y},\profile, \bar{\w}) -  s(x^{*}; \profile, \bar{\w}).
\end{align}

Intuitively the quantity $\MMR - \tau_{1} = \max_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w) - \min_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w)$ estimates the contribution to regret of our uncertainty about the weights $\w$, while $\MMR - \tau_{2} $ estimates the uncertainty about the profile.
Therefore, whenever ${\color{red} \lambda *} \tau_{1} < \tau_{2}$ we ask a question to the chair, and compare component-wise $\bar{\w}$ and $\w^{\tau}$, the argmax of Eq. (\ref{eq:tau1}), to find the position $r$ that is most valuable to ask about (the one that maximizes $\abs{\bar{\w}_r - \w^{\tau}_r}$), and choose $\lambda$ as the middle of the interval of possible values for that rank.
Instead, if $\tau_{1} > \tau_{2}$ we ask a question to one of the agents. We select the question by checking for each agent $j$ the difference between the difference of the ranks of $x$ and $y$ in the profile that minimizes compared to the one that maximizes the difference of scores, and pick an agent related to the highest difference, then pick $x$ or $y$ with $1/2$ chances as the first alternative of the question, and pick an incomparable alternative equiprobably as the second one.

The \strat{Pessimistic} strategy selects the question that leads to minimal regret in the worst case, considering both possible answers to the question. Assume that a question leads to the possible new knowledge states $(\pprofile_1, W_1)$ and $(\pprofile_2, W_2)$, depending on the answer. Then the badness of the question in the worst case is:
\[\max_{i=1,2} \MMR(\pprofile_i,W_i) \]
This badness measure gives a way of picking questions among a set of possible questions, by picking one that minimizes the measure. Note that other aggregators than $\max$ can be used as well. 
%The \strat{Pessimistic} strategy considers as possible questions the ones defined by the \strat{Random} strategy (with the difference that a threshold is used: if for some rank $r$ the interval of possible values for $\lambda$ is not larger than $0.1$, the question is not considered). 
It uses the $\leximax$ criterion %a variant of the $\max$ 
as an aggregator: if the maximal $\MMR$ of two questions are equal, then it considers the other $\MMR$ values, that are the one associated to the opposite answer, preferring the question with the lowest of this value.
 We expect this strategy to perform very well, but only for very small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute $\MMR$ twice, whose complexity is $O(nm^3)$. For small dimensions, it gives us an estimate of an upper bound to the possible quality of a strategy.

>>>>

%We also define the \strat{Extreme completions} strategy, which we consider as a more realistic baseline. 
%Consider the solution of the minimax regret game, 
% $(x^{*},\bar{y},\bar{\profile},\bar{\w})$, where $x^{*}$ is the minimax regret optimal alternative, and $\bar{y} = \arg \max_{y \in A} \PMR(x,y; \pprofile, W)$, $\bar{\profile}$ and $\bar{\w}$ are the adversarial choices, thus, the instantiations that, given the choice of $x^*$, maximize the regret. 
%Define: 
%\begin{align}
%\tau_{1} & = \min_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w),  \label{eq:tau1} \\
%\tau_{2} & = \min_{\profile \in C(\pprofile)} s(\bar{y},\profile, \bar{\w}) -  s(x^{*}; \profile, \bar{\w}).
%\end{align}

%Intuitively the quantity $\MMR - \tau_{1} = \max_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w) - \min_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w)$ estimates the contribution to regret of our uncertainty about the weights $\w$, while $\MMR - \tau_{2} $ estimates the uncertainty about the profile.
%Therefore, whenever ${\color{red} \lambda *} \tau_{1} < \tau_{2}$ we ask a question to the chair, and compare component-wise $\bar{\w}$ and $\w^{\tau}$, the argmax of Eq. (\ref{eq:tau1}), to find the position $r$ that is most valuable to ask about (the one that maximizes $\abs{\bar{\w}_r - \w^{\tau}_r}$), and choose $\lambda$ as the middle of the interval of possible values for that rank.
%Instead, if $\tau_{1} > \tau_{2}$ we ask a question to one of the agents. We select the question by checking for each agent $j$ the difference between the difference of the ranks of $x$ and $y$ in the profile that minimizes compared to the one that maximizes the difference of scores, and pick an agent related to the highest difference, then pick $x$ or $y$ with $1/2$ chances as the first alternative of the question, and pick an incomparable alternative equiprobably as the second one.

The \strat{Pessimistic} strategy selects the question that leads to minimal regret in the worst case, considering both possible answers to the question. Assume that a question leads to the possible new knowledge states $(\pprofile_1, W_1)$ and $(\pprofile_2, W_2)$, depending on the answer. Then the badness of the question in the worst case is: $\max_{i=1,2} \MMR(\pprofile_i,W_i)$.
This badness measure gives a way of picking questions among a set of possible questions, by picking one that minimizes the measure. %Note that other aggregators than $\max$ can be used as well. 
%The \strat{Pessimistic} strategy considers as possible questions the ones defined by the \strat{Random} strategy (with the difference that a threshold is used: if for some rank $r$ the interval of possible values for $\lambda$ is not larger than $0.1$, the question is not considered). 
However, to avoid the absorption property of max, we adopt the $\leximax$ criterion %a variant of the $\max$ 
as an aggregator: if the maximal $\MMR$ of two questions are equal, then it considers the other $\MMR$ values, (the ones associated to the opposite answer), preferring the question with the lowest of this value.
 We expect this strategy to perform very well, but only for very small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute $\MMR$ twice, whose complexity is $O(nm^3)$. For small dimensions, it gives us an estimate of an upper bound to the possible quality of a strategy.

 The \strat{LimitedPessimistic} strategy uses the same criterion as the pessimistic strategy, but only considering a small set of candidate questions.
For each voter, a candidate question is chosen by considering the heuristic proposed by Lu and Boutilier \cite{Lu2011}. 
For the chair, we define
\begin{align}
\tau & = \min_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w),  \label{eq:tau1} 
\end{align}
and compare component-wise $\bar{\w}$ and $\w^{\tau}$, the argmax of Eq. (\ref{eq:tau1}), to find the position $r$ that is most valuable to ask about (the one that maximizes $\abs{\bar{\w}_r - \w^{\tau}_r}$), and choose $\lambda$ as the middle of the interval of possible values for that rank.

We then evaluate, for each candidate question, the minimax regret for each possible answer; finally we choose the best according to $\leximax$.
